\documentclass[10pt]{article}
\usepackage{amsmath, amsthm, amssymb}
\usepackage{graphicx}
% soul's needed for textst to cross out todo items
\usepackage{soul}
%\usepackage{lootex}
\usepackage{amssymb}
\usepackage{epstopdf}
\title{Polynome June 2009}
%\author{Franziska Hinkelmann}
%\date{April 17, 2008}
\pagestyle{empty}
\begin{document}
%\maketitle
%\thispagestyle{empty}

\noindent
\subsection*{Newest Todos}
\textbf{use multiple input data files}
\begin{itemize}
    \item user uploads one file or data in data field with multiple time
    series separated by \#\#\#
    \item don't allow blank lines, return warning
    \item modify data\_has\_correct\_format to check for lines beginning with
    hash symbols
    \item write routine splitting up data file after checking, return list of
    filenames, \$file-prefix.datafile\$i.txt
    \item modify .pl scripts to accept and return list of files instead of one
    file
    \item M2 should receive string with list of filenames
    \item pass list of filenames to M2 scripts (discretize.m2)
\end{itemize}


\subsection*{Other Todos}
\begin{itemize}
    \item put svn head on polymath but in a different folder \/tmp 
    \item put EA under revision control $\Rightarrow$ \textbf{Brandy}
    \item make sure correct \$PATH is set $\Rightarrow$ \textbf{Franzi}
    \item make html form as table instead of using spaces by alignment
    \item \textit{Analysis of State Space} is put in a table ( $\Rightarrow$
    \textbf{Mike}) and should only be printed, if \$show\_statespace is set
    \item \textst{rename ffilename, display function file name in polynome}
    \item \textst{need to change the logical structure: If user wants wiring
    diagram and functions, we need to use a different method}
    \item \textst{change names of files that are created, right now it's too long
    $\Rightarrow$ \textbf{Mike}}
    \item \textst{need check whether number of nodes $==$ number of nodes in
    data $\Rightarrow$ \textbf{Franzi}}
    \item add check for update schedule to user interface $\Rightarrow$
    \textbf{Franzi}
    \item give user more feedback about whether calculation worked/crashed/done 
    \item make sure there are error messages (e.g., ccomps not found or file not 
            writable) 
    \item find safe way of uploading files, maybe it's ok for now 
    \item can we distinguish between deterministic and stochastic models? -
    Yes, but it is not implemented right now for some reason $\Rightarrow$
    \textbf{We'll implement this once EA is on there, there were problems with
    the output}
    \item change JavaScript Rollover for "Type of Simulation", or all of them
    $\Rightarrow$ \textbf{Brandy}
    \item create synchronuous model but simulate with sequential updates
    (compare to work on Fruit Fly by Sontag and Chavez)
\end{itemize}
\subsection*{Priority - is this all for the paper submitted in April?}
\begin{itemize}
	\item React with parameters
	\item multiple data set
	\item standalone for react (and maybe simulation)
	\item modify Discretization to allow threshold (or other parameters)
    \item multistate
    \item Pandapas and diBernardo data set
\end{itemize}
\section*{DIMACS}
Polynome: 
\begin{itemize}
    \item \textst{last done: why is show\_functions not working?}
    \item Question: should functions called from polynome.pl return an error
    code or die (status quo, e.g., create\_input\_data.pl)?
    \item \textst{trying to run a perltidy on all files ( to format them ) - should we
    decide on a coding style?}
    \item maybe we can use strict everywhere to ensure proper coding, done so
    far for polynome.pl, should do it for everything
    \item \textst{remove all of the commented code.  I can't tell what is
    really not needed, and what might be useful in the future.}
    \item use css.  \textst{Also, use multi-line 'print's for the html.}
    \item write a routine: check\_data: inputs include the file, pvalue, nnodes.
    Perhaps a display as to the nature of the file could be displayed too:
    e.g: There are 13 time series data, with knockout data for ...\\
    check routines\\
     p\_value, n\_nodes: are they numbers and allowed numbers?\\
     is number of nodes equal to number of columns in data? is data in number format\\
     print out number of lines in data\\
\\
     if sequential update is chosen, is the updateschedule valid?\\
     check for number of elements in schedule\\
     sort -u the array, then a[1]=1 and a[n]=n\\
     warning if update schedule but not sequential update\\

    $\Rightarrow$ \textbf{Franzi}
    \item \textst{The list of components, and their features should be a
    table.}
    \item \textst{links to tutorial and tip help should be local.}
    \item \textst{there is a hardcoded ref to /Users/fhinkel/Sites.}
    \item Perhaps all files associated to a clientip should be in one
    directory? - Yes!
    \item  \textst{change the names of dgfilename, ffilename, ...}
    \item  \textst{Have the main function determine the functional extent of the buttons.  The
    inner code should not be checking for hardcoded strings?}
    \item \textst{Remove message from website about constant functions}
    \item \textst{Remove hard coded links to tutorial}
    \item return feedback on functions/data (i.e., "you entered 3 time courses
    of lenght ...)
    \item \textst{cronjob in Polynome to delete old files}
    \item multiple data $\Rightarrow$ \textbf{Brandy}
    \item code design-modularity: Can we get a "coding" grant? NSF?
    \item web userstatistics, or registration for users
    \item \textst{window refresh}
    \item \textst{revision control}
    \item apache-stop process-script to kill: need a solution, also ned
    solution if script runs too long
    \item webmaster - user support A
    \item extend to multistate
    \item Paper for more visible journal: Bioinformatics
    \item boolean $\rightarrow$ nonboolean
    \item allow to input functions in addition to data
    \item partial statespace + stats - partial view (prob $> y$)
    \item bio information: e.g., activation/inhibition in wiring diagram
    $\rightarrow$ need definition of \textit{Boolean inhibitor} (threshold?
    \cite{Edwards:symbolic} computationally describe this set of functions ) and then
    algorithm $\Rightarrow$ this is a PhD problem!
    \item bio syst-application: DiBernardo?
    \item dynamic programming: to evaluate functions more efficientlyA
    \item Large network limitation: maybe sampling? Alan's reduction method?
    \item Polymath $\rightarrow$ Polynome
    \item \textst{User interface: Boolean data, don't reset to default}
    \item partial view
    \item more than one time course
    \item currently no user options
    \item NCF
    \item parallelization
    \item status of EA
    \item DREAM
    \item more extensive tutorial
    \item detailed example
    \item explore the probability of including coding theory alg
\end{itemize}
\section*{DREAM}
\begin{itemize}
    \item Paola not
    \item Abdul maybe for NCF
    \item Small, focused teams 
    \item meeting August 20-22 at MBI
\end{itemize}
%-------------------------------------------
%\newpage
%\bibliographystyle{plain}

% the appear in the order they are referenced
\bibliographystyle{unsrt}
%\bibliographystyle{../h-physrev3}
\bibliography{../phd}

\end{document}
